\documentclass[12pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{enumitem}
\setlist{topsep=2pt, itemsep=1pt}
\geometry{margin=.5in}

\title{Room2Room}
\author{
    Owen Monus \and
    Cole Yager \and
    Pawan Kshetri \and
    Weicheng Wang \and
    Pushpinder Singh \and
    Esteban Perez Mendoza
    }
    \date{January 23rd, 2026}
    
\begin{document}
\maketitle
\pagenumbering{gobble}

\section*{Problem Description}
\paragraph{} In university housing, students living away from home struggle to buy and sell dorm
furnishings due to quick semester changeovers and a lack of transportation access. This
causes students to buy and sell items at pawn shops and online marketplaces where sellers
are trying to make money, not help students. This adds stress to students, who are already
financially burdened and are typically on a short timeline to move in or out before the
next semester begins. The goal of this project is to create an online marketplace where
students can buy and sell housing furnishings to other students at the same campus,
eliminating transportation issues and allowing students to support other students.

\section*{User Roles}

\subsection*{1. Buyer}
\subsubsection*{Main Functional Requirements}
\begin{enumerate}[label=\arabic*.]
    \item Buyer can view and search for items.
    \item Buyer can use filters to view and sort listings by category, condition, and price.
    \item Buyer can communicate with a seller for more details about a certain listing.
    \item Buyer can communicate with more than one seller regarding more than one listing at a time.
    \item Buyer can receive email alerts if seller responds to their messages.
    \item Buyer can save listings to view at a later time.
    \item Buyer has a profile where they can save listings and access their chats.
\end{enumerate}

\subsubsection*{Main Quality Requirements}
\begin{enumerate}[label=\arabic*.]
    \item Robustness: The system should handle
          empty searches, and display an adequate, informative message when an invalid search
          has been made. If for some reason an invalid combination of filters is applied - such
          as filtering to listings less than zero dollars - the system should handle the invalid
          filter state and provide the user with a message indicating no listings found.

    \item Time Efficiency: When searching and filtering through listings, the page
          must load within 2 seconds. When communicating with sellers, messages should send
          immediately and messages from the seller should be fetched every 15 seconds. The buyer
          should receive emails notifying them of seller communication within 2 minutes of the
          server receiving a message from the seller. When viewing a listing, the page should
          load in less than 4 seconds including images. When a buyer saves a listing for later,
          it should be almost instant. The buyer should also be able to load their profile and
          access their saved items and chats in less than 5 seconds.

    \item Correctness: If a seller marks an item as sold while the buyer is viewing an item, this
          should be reflected immediately on the buyer's end without needing to refresh the page. When a
          buyer searches for a listing, the search should be deterministic and accurate. The
          filters should work properly in conjunction with a search. When a buyer is
          communicating with a seller, their messages go to the intended recipient only. When a
          buyer receives a message, it is displayed from the correct sender. Upon saving a
          listing, that listing is saved on the buyers account only. A buyer should not receive
          an email intended for another user.
\end{enumerate}

\subsection*{2. Seller}
\subsubsection*{Main Functional Requirements}
\begin{enumerate}[label=\arabic*.]
    \item Seller can create a listing. (must specify category, conditions, price).
    \item Seller can edit a listing (includes on hold, sold, other modifications to existing listing).
    \item Seller can delete a listing.
    \item Seller can communicate with a buyer to give more details about a listing.
    \item Seller can communicate with more than one buyer regarding more than one listing at a time.
    \item Seller can receive email alerts for communication with buyers.
    \item Seller has a profile where they can see their listings and access their chats.
\end{enumerate}

\subsubsection*{Main Quality Requirements}
\begin{enumerate}[label=\arabic*.]
    \item Robustness: The system should provide field validation when making a listing. If the
          seller misses filling mandatory fields (such as category, conditions, price), they
          should not be able to create the listing. The system should prevent a listing from
          being edited into an invalid state, such as having a negative price, or no category.
          The system should handle photo uploads of various file types and ensure the image is
          not too large to facilitate quick saving. The system should present the seller 
          with informative error messages indicating the error state.

    \item Time Efficiency: Seller should be able to post a listing within 5 seconds. Attached
          pictures should upload quickly - within 2 seconds per picture. The UI for making a
          listing should feel responsive, and all loading screens should be less than 5 seconds.
          Editing a listing should take less than 2 seconds. The seller should be able to load
          their profile within two seconds. When communicating with buyers, messages should send
          immediately and messages from the buyer should be fetched every 15 seconds. The seller
          should receive emails notifying them of buyer communication within 2 minutes of the
          server receiving a message from the buyer.

    \item Correctness: A seller's listing should be presented to buyers in the exact way they
          created it. Any modifications to a listing made by a seller should update immediately
          so buyers see the most up to date information. When a seller uploads images, the
          images should be stored without loss of data. The images should be able to be
          retrieved at a later time. When a seller deletes a listing, only the selected listing
          is deleted. When a seller is communicating with a buyer, their messages go to the
          intended recipient only. When a seller receives a message, it is displayed from the
          correct sender. A seller should not receive an email intended for another user.
\end{enumerate}

\end{document}